Fig6

### 2020-03-29 analysis/figure-6.Rmd
now with better fig 3 and 6

hypvsd <- getcandidatevsd(candidategenesslim, "hypothalamus", sexlevels)
pitvsd <- getcandidatevsd(candidategenesslim, "pituitary", sexlevels)
gonvsd <- getcandidatevsd(candidategenesslim, "gonad", sexlevels)
head(hypvsd)
head(pitvsd)
head(gonvsd)

@@

@@

```{r fig6, fig.height=7, fig.width=7}
makeboxplotsmanip <- function(df, whichgene, mysubtitle, whichsex, whichtimepoint){
  p <- df %>%
    filter(treatment %in% alllevels,
           gene %in% whichgene,
           sex %in% whichsex) %>%
    filter(treatment %in% whichtimepoint) %>%
    ggplot(aes(x = treatment, y = counts, fill = treatment, color = sex)) +
    geom_boxplot(outlier.shape = NA) + 
    geom_jitter(size = 0.5, width = 0.1) +
    facet_wrap(~gene, scales = "free_y", nrow = 1) +
    theme_B3() +
    scale_fill_manual(values = allcolors) +
    scale_color_manual(values = allcolors) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = "none",
          plot.caption = element_text(face = "italic")) +
    labs(y = "gene expression" , x = "Parental Stages and Manipulations", subtitle = mysubtitle) +
    theme(strip.text = element_text(face = "italic"))
  return(p)
}

## hyp 
a2 <- makeboxplotsmanip(hypvsd, c("DRD1","EGR1","PRLR"), "Female hypothalamus", "female",
                  c("inc.d3", "m.inc.d3", "inc.d17", "m.inc.d17",  "hatch", "m.n2"))  +
  theme(axis.title.x = element_blank())
b2 <- makeboxplotsmanip(hypvsd, c("BDNF","ESR2", "FOS"), " ", "female",
                  c("inc.d3", "m.inc.d3", "inc.d17", "m.inc.d17"))  +
  theme(axis.title.x = element_blank())

@@

f1 <- makeboxplotsmanip(hypvsd, c("DRD1", "EGR1", "PRLR"), "Male hypothalamus", "male",
                  c( "inc.d17", "m.inc.d17", "hatch", "m.n2"))  +
  theme(axis.title.x = element_blank())

f2 <- makeboxplotsmanip(hypvsd, c( "PRL"), " ", "male",
                  c( "inc.d17", "m.inc.d17", "hatch", "m.n2"))  +
  theme(axis.title = element_blank())

h <- makeboxplotsmanip(hypvsd, c("AR", "AVP", "BDNF", "ESR1", "LBH"), " ", "male",
                  c( "inc.d17", "m.inc.d17"))  + labs(caption = " ")

i <- makeboxplotsmanip(hypvsd, c("GNRH1"), " ", "male",
                  c("hatch", "m.n2"))  +
  theme(axis.title = element_blank()) +
  labs(x = " ",
       caption = "Candidate genes that were not differentially expressed following removal: AVPR1B, AVPR2, ESR1, GNRHR, VIP")

ab2 <- plot_grid(a2,c, rel_widths = c(18,5), labels = "auto", label_size = 8)
cde <- plot_grid(b2,d,e, rel_widths = c(12,6,2), nrow =  1, align = "h",  
                 labels = c("c", "d", " "), label_size = 8)
f12 <- plot_grid(f1,f2, rel_widths = c(3,1), labels = c("e",  " "), label_size = 8)
hi <- plot_grid(h,i, ncol = 2, rel_widths = c(10,2),labels = c("f",  "g"), label_size = 8, align = "h")

plot_grid(ab2, cde, f12,hi, nrow = 4, rel_heights = c(1,1,1,1.25))

>>>>

hypvsd <- getcandidatevsd(candidategenesslim, "hypothalamus", sexlevels)
pitvsd <- getcandidatevsd(candidategenesslim, "pituitary", sexlevels)
gonvsd <- getcandidatevsd(candidategenesslim, "gonad", sexlevels)

@@

```{r boxplotfunction}
makeboxplotsmanip <- function(df, whichgene, mysubtitle, whichsex, whichtimepoint){
  p <- df %>%
    filter(treatment %in% alllevels,
           gene %in% whichgene,
           sex %in% whichsex) %>%
    filter(treatment %in% whichtimepoint) %>%
    ggplot(aes(x = treatment, y = counts, fill = treatment, color = sex)) +
    geom_boxplot(outlier.shape = NA) + 
    geom_jitter(size = 0.5, width = 0.1) +
    facet_wrap(~gene, scales = "free_y", nrow = 1) +
    theme_B3() +
    scale_fill_manual(values = allcolors) +
    scale_color_manual(values = allcolors) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = "none",
          plot.caption = element_text(face = "italic")) +
    labs(y = "gene expression" , x = "Parental Stages and Manipulations", subtitle = mysubtitle) +
    theme(strip.text = element_text(face = "italic", size = 5)) + 
    scale_y_continuous(labels = scales::number_format(accuracy = 1))
  return(p)
}
```

@@

```{r fig6, fig.height=8, fig.width=10}

## hypothatlamus
a <- makeboxplotsmanip(hypvsd, c("DRD1","EGR1","PRLR"), "Female hypothalamus", "female",
                  c("inc.d3", "m.inc.d3", "inc.d17", "m.inc.d17",  "hatch", "m.n2"))  +
  theme(axis.title.x = element_blank())
b <- makeboxplotsmanip(hypvsd, c("BDNF","ESR2", "FOS"), " ", "female",
                  c("inc.d3", "m.inc.d3", "inc.d17", "m.inc.d17"))  +
  theme(axis.title = element_blank())

@@

f <- makeboxplotsmanip(hypvsd, c("DRD1", "EGR1", "PRLR"), "Male hypothalamus", "male",
                  c( "inc.d17", "m.inc.d17", "hatch", "m.n2"))  +
  theme(axis.title.x = element_blank())

g <- makeboxplotsmanip(hypvsd, c( "PRL"), " ", "male",
                  c( "inc.d17", "m.inc.d17", "hatch", "m.n2"))  +
  theme(axis.title = element_blank())

h <- makeboxplotsmanip(hypvsd, c("AR", "AVP", "BDNF", "ESR1", "LBH"), " ", "male",
                  c( "inc.d17", "m.inc.d17")) +
  theme(axis.title = element_blank())

i <- makeboxplotsmanip(hypvsd, c("GNRH1"), " ", "male",
                  c("hatch", "m.n2"))  +
  theme(axis.title = element_blank())

j <- makeboxplotsmanip(pitvsd, c("AR", "PRL", "LBH"), "Female pituitary", "female",
                  c( "inc.d17", "m.inc.d17", "hatch", "m.n2"))  + theme(axis.title.x = element_blank())

k <- makeboxplotsmanip(pitvsd, c("DRD1"), " ", "female",
                  c( "inc.d3", "m.inc.d3"))  + theme(axis.title = element_blank())

l <- makeboxplotsmanip(pitvsd, c("BDNF", "PRLR"), " ", "female",
                  c( "inc.d17", "m.inc.d17"))  +  theme(axis.title = element_blank())

m <- makeboxplotsmanip(pitvsd, c("AVPR1B", "AVPR2", "EGR1", "GNRHR", "JUN"), " ", "female",
                  c("hatch", "m.n2"))  + theme(axis.title = element_blank())

n <- makeboxplotsmanip(pitvsd, c("LBH"), "Male pituitary", "male",
                  c("inc.d17", "m.inc.d17", "hatch", "m.n2"))  
o <- makeboxplotsmanip(pitvsd, c("DRD1", "ESR2"), " ", "male",
                  c("inc.d17", "m.inc.d17"))  + theme(axis.title  = element_blank())
p <- makeboxplotsmanip(pitvsd, c("AVPR1A", "PRLR"), " ", "male",
                  c("hatch", "m.n2"))  + theme(axis.title  = element_blank())

q <- makeboxplotsmanip(gonvsd, c("LBH"), "Male gonads ", "male",
                  c("inc.d17", "m.inc.d17"))  + theme(axis.title  = element_blank())
r <- makeboxplotsmanip(gonvsd, c("JUN"), "Female gonads ", "female",
                  c("inc.d17", "m.inc.d17"))  + theme(axis.title  = element_blank())

abcd <- plot_grid(a,b,c,d,e, nrow = 1, rel_widths = c(16,10,4,6,2), align = "h", labels = c("a", "b", "c", "d"), label_size = 8)
efgh <- plot_grid(f,g,h,i, nrow = 1, rel_widths = c(10,3,10,2), align = "h", labels = c("e", " ", "f", "g"), label_size = 8)
jklm <- plot_grid(j,k,l,m, nrow = 1, rel_widths = c(12,2,4,10), align = "h",  labels = c("h", "i", "j", "k"), label_size = 8)
nopqr <- plot_grid(n,o,p,q,r, nrow = 1, rel_widths = c(4,4,4,2,2), align = "h",  labels = c("l", "m", "n", "o", "p"), label_size = 8)

plot_grid(abcd, efgh, jklm,nopqr, ncol = 1)
```
